A Container-Based Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-10-15 draft.tex
Update draft.tex

\subsection{Event Driven Model} 
\label{edm}
Based on a reactive architecture we proposed in a previous work
\cite{guervos2018introducing}, we now describe the general architecture shown in
Figure \ref{fig:kafkEO}. Again, we can explain the model using the analogy
of producers and consumers of messages. First, we can see that
there are two queues, one labeled \texttt{Input}, and the other one \texttt{Output}. In the diagram, 
push operations on a queue are represented by solid arrows connecting to the left side
of the queue box, and pull or pop operations as solid arrows leaving from the right side.
Also, the architecture has at least four processes indicated in the diagram as
swimlanes: First, the \texttt{Setup} process, responsible for the reading a configuration
file, and creating the initial populations. Second, the \texttt{Controller} process,
responsible for the migration between populations, and keeping track of the
iterations of the algorithm. The \texttt{Message Queue} process runs the \texttt{Input} and \texttt{Output}
queues. Finally, there is at least one \texttt{Stateless Function} process responsible
for running the isolated algorithms. In the example, two processes \texttt{PSO} and \texttt{GA},
are shown.

The algorithm starts with the \texttt{Setup} process pulling a configuration message from
the \texttt{Experiments} queue, this is not shown in the diagram. The configuration message 
includes all the parameters needed to execute the algorithm, among other things,
the number of populations, the number of individuals, and the number of iterations
of the algorithm. We give more details about the configuration data structure
in Section \ref{experiment_flow}. % Missing  % added 
Once the configuration is read, we can follow the path of 
messages as follows:

@@

\item Each population is then pushed to the \texttt{Input} queue, so they can be consumed 
by Stateless functions responsible for the execution of the search.

\item One or more \texttt{Stateless functions} are constantly pulling population messages
from the \texttt{Input} queue. Taking the population data and metadata as parameters, these 
functions are responsible for the actual execution of the optimization algorithm. 
They take the current state of the population and run the algorithm for a certain 
number of iterations.

\item Once they finish the execution, the population state
is packed again along with additional metadata about the execution of the algorithm.
The resulting populations are now pushed to the Output queue. Once finished, another 
population is pulled from the queue.

\item The \texttt{Controller} process is responsible for keeping track of the progress of 
the search. It pulls current populations from the \texttt{Output} queue, inspects the metadata 
and if an optimal solution has been found or the maximum number of iteration has been
reached it signals the stop of the execution.

\item Otherwise, it passes the stream of messages 
to a migration process, where populations are mixed with each other. New populations 
are generated from this migration, and they are again pushed to the Input queue to continue 
in a loop. The \texttt{Controller} is also responsible of logging the metadata received with the
messages.  
\end{enumerate}

>>>>

\subsection{Event Driven Model} 
\label{edm}
Based on a reactive architecture we proposed in a previous work
\cite{guervos2018introducing}, we now describe the general architecture shown in
Figure \ref{fig:kafkEO}. Again, we can explain the model using the analogy
of producers and consumers of messages. First, we can see two queues, 
one labeled \texttt{Input} and the other one \texttt{Output}. In the diagram, 
push operations on a queue are represented by solid arrows connecting to the left side
of the queue box, and pull or pop operations as solid arrows leaving from the right side.
The architecture has at least four processes indicated in the diagram as
swimlanes: First, the \texttt{Setup} process, responsible for the reading a configuration
file and creating the initial populations. Second, the \texttt{Controller} process,
responsible for the migration between populations and keeping track of the algorithm's
iterations. The \texttt{Message Queue} process runs the \texttt{Input} and \texttt{Output}
queues. Finally, there is at least one \texttt{Stateless Function} process responsible
for running the isolated algorithms. In the example, two processes \texttt{PSO} and \texttt{GA},
are shown.

The algorithm starts with the \texttt{Setup} process pulling a configuration message from
the \texttt{Experiments} queue (not shown in the diagram). The configuration message 
includes all the parameters needed to execute the algorithm, the number of populations,
the number of individuals, and the number of iterations 
of the algorithm. We give more details about the configuration data structure
in Section \ref{experiment_flow}. % Missing  % added 
Once the configuration is read, we can follow the path of 
messages as follows:

@@

\item Each population is then pushed to the \texttt{Input} queue, so that they can be consumed 
by stateless functions responsible for the search's execution.

\item One or more \texttt{Stateless functions} are constantly pulling population messages
from the \texttt{Input} queue. They take the current state of the population and 
run the algorithm for a certain number of iterations.

\item Once they finish the execution, the population state
is packed again with additional metadata about the algorithm's execution.
The resulting populations are now pushed to the Output queue. Once finished, another 
population is pulled from the queue.

\item The \texttt{Controller} process is responsible for keeping track of the progress of 
the search. It pulls current populations from the \texttt{Output} queue, inspects the metadata, 
and if an optimal solution has been found or the maximum number of iteration has been
reached, it signals the stop of the execution.

\item Otherwise, it passes the stream of messages 
to a migration process, where populations are mixed. New populations 
are generated from this migration and again pushed to the Input queue to continue 
in a loop. The \texttt{Controller} is also responsible for logging the metadata received with the
messages.  
\end{enumerate}
